---
title: "Happiness Project"
author: "Andy"
date: "3/13/2022"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float:
      smooth_scroll: false
---

<br>  

# Project Description

<br>  

<font size="3">   The data was collected from Gallup World Poll. Their survey consisted of questions that asked participants to rank their own life on a Cantril ladder with a scale from 1 to 10, 10 being the best ideal way of living and 0 being the worst. This data set focuses on the happiness score of each country, which ranges from 0 to 10. Each country is ranked based on that averaged happiness score for participants. The team recorded scores for these factors: economy or GDP per Capita, family or social support, health or life expectancy, and freedom to help explain the happiness score of each country. </font>

<font size = "5">**Goals**</font>

  1. <font size = "3">**Data Manipulations**
      - Merge the data with 2 other data sets
          - Death Data: Total annual number of deaths by country/risk factor
          - UN Country Data: Indicators of all the countries present in UN Data
  2. **Various visualizations using ggplot2**
      - Happiness Rankings throughout countries
      - Change in happiness rankings
  3. **Statistical Analysis**
      - Linear Regressions & Multiple Regressions
      - Clustering
      - Time Series</font>

<br>  


```{r, results='hide', message=FALSE}
library(socviz)
library(lubridate)
library(geofacet)
library(ggthemes)
library(ggrepel)
library(ggridges)
library(plyr)
library(skimr)
library(tidyverse)
library(gganimate)
library(plotly)
theme_set(theme_minimal())
library(stargazer)  # regression tables
library(ggstatsplot)
```

<br>  

# Data Wrangling

---


<br>  

## Happiness Data

```{r, echo=TRUE, warning=FALSE, message=FALSE}
# Read 2015 Data
h15 <- read_csv("Happiness_Data/2015.csv")
h15 <- h15 %>%
  dplyr::mutate(Year = 2015) %>%
  dplyr::rename(H_rank=`Happiness Rank`, # Modify variable names
                H_score = `Happiness Score`,
                GDP=`Economy (GDP per Capita)`,
                Health=`Health (Life Expectancy)`,
                Trust=`Trust (Government Corruption)`,
                SE=`Standard Error`,
                dystopia_res = `Dystopia Residual`) 


# Read 2016 Data
h16 <- read_csv("Happiness_Data/2016.csv")  
h16 <- h16 %>%
  dplyr::mutate(Year = 2016,
      `Standard Error` = (`Upper Confidence Interval`-`Lower Confidence Interval`)/3.92) %>%
              # SE = (upper limit – lower limit) / 3.92. 
              # This is for 95% CI
  dplyr::select(-c(`Upper Confidence Interval`,`Lower Confidence Interval`)) %>%
  dplyr::rename(H_rank=`Happiness Rank`, # Modify variable names
                H_score = `Happiness Score`,
                GDP=`Economy (GDP per Capita)`,
                Health=`Health (Life Expectancy)`,
                Trust=`Trust (Government Corruption)`,
                SE=`Standard Error`,
                dystopia_res = `Dystopia Residual`)



# Since we don't have a variable 'Region' starting from 2017, we will create it for 
# each year
h_regions <- dplyr::select(h16, Country, Region)



# Read 2017 Data
h17 <- read_csv("Happiness_Data/2017.csv")  
h17 <- h17 %>%
  dplyr::mutate(Year = 2017,
                `Standard Error` = (`Whisker.high`-`Whisker.low`)/3.92,) %>%
  merge(h_regions,by="Country", all.x=T) %>%
  dplyr::select(-c(`Whisker.high`,`Whisker.low`)) %>%
  dplyr::rename(H_rank=`Happiness.Rank`, # Modify variable names
                H_score = Happiness.Score,
                GDP=Economy..GDP.per.Capita.,
                Health=Health..Life.Expectancy.,
                Trust=Trust..Government.Corruption.,
                SE=`Standard Error`,
                dystopia_res = Dystopia.Residual)


# Read 2018 Data
h18 <- read_csv("Happiness_Data/2018.csv")  
h18 <- h18 %>%
  dplyr::mutate(Year = 2018) %>%
  dplyr::rename(H_rank=`Overall rank`, # Modify variable names
                H_score = `Score`,
                GDP=`GDP per capita`,
                Country = `Country or region`,
                Health=`Healthy life expectancy`,
                Trust=`Perceptions of corruption`,
                Freedom = `Freedom to make life choices`,
                Family = `Social support`) %>%
  merge(h_regions,by="Country", all.x=T) %>%
  dplyr::mutate(dystopia_res = H_score - (GDP + Family + Health + Freedom + Generosity + as.numeric(Trust)))



# Read 2019 Data
h19 <- read_csv("Happiness_Data/2019.csv")  
h19 <- h19 %>%
  dplyr::mutate(Year = 2019) %>%
  dplyr::rename(H_rank=`Overall rank`, # Modify variable names
                H_score = `Score`,
                GDP=`GDP per capita`,
                Country = `Country or region`,
                Health=`Healthy life expectancy`,
                Trust=`Perceptions of corruption`,
                Freedom = `Freedom to make life choices`,
                Family = `Social support`) %>%
  merge(h_regions,by="Country", all.x=T) %>%
  dplyr::mutate(dystopia_res = H_score - 
                  (GDP + Family + Health + Freedom + Generosity + as.numeric(Trust)))

# Combine all data into all_dat
h_alldat <- tibble(rbind.fill(h15,h16,h17,h18,h19))
h_alldat <- h_alldat %>%
  dplyr::mutate(Country = as.factor(tolower(Country)),
                Region = as.factor(Region))

#rmarkdown::paged_table(h_alldat)
save(h_alldat, file = 'h_alldat.RData')
knitr::kable(papeR::summarize_numeric(h_alldat, type = "numeric", group = "Region",variables = c("H_rank", "H_score"),  test = FALSE))

```

<br>  

## Death & Risk Factors Data
```{r, echo=TRUE, warning=FALSE, message=FALSE}
# Read data in
death_dat <- read_csv('/Volumes/Programming/Spring 2022/DANL 310/my_website/aLin-96.github.io/Happiness_Data/number-of-deaths-by-risk-factor.csv')

death_dat <- death_dat %>%
  filter(Year > 2015) %>%
  arrange(Year)

rmarkdown::paged_table(death_dat)
```
<br>  


## Country Profile UN Data
```{r, echo=TRUE, warning=FALSE, message=FALSE}
country_profile <- read_csv('/Volumes/Programming/Spring 2022/DANL 310/my_website/aLin-96.github.io/Happiness_Data/kiva_country_profile_variables.csv')

country_profile <- country_profile %>%
  dplyr::mutate(country = tolower(country)) %>%
  dplyr::rename(Country = country) %>%
  dplyr::select(-c(Region))

h_p_alldat <- merge(h_alldat, country_profile, by = "Country")

rmarkdown::paged_table(country_profile)
```
<br>

## TOP 10 AVG Hppiness Scores (2015 ~ 2019)

```{r, echo = TRUE, eval = TRUE, warning = FALSE}
# Get Top 10 mean of happiness rank from 2015 ~ 2019

top_10 <- h_alldat %>%
  group_by(Country) %>%
  dplyr::summarise(mean_rank = mean(H_rank)) %>%
  arrange(desc(mean_rank)) %>%
  filter(mean_rank <= 10)

rmarkdown::paged_table(top_10)
```

<br>  
<br>  
<br>  

# Visualizations

---

<br>  


## Boxplot of Happiness Scores in different Regions

```{r}
ggplot(dplyr::filter(h_alldat, Region != "NA")) +
  geom_boxplot(aes(x = H_score, y=reorder(Region, H_score), color = Region))+
  theme_classic() +
  theme(legend.position = "None") +
  labs(x = "Happiness Scores", y = "Regions")
```

<br>  

## Happiness Scores vs GDP 


```{r}
ggplot(dplyr::filter(h_alldat, Region != "NA"), aes(x = GDP, y=H_score, color = Region)) +
  geom_point() +
  theme_classic()+
  labs(title = "Happiness Scores vs GDP by Region\n")

```
<br>  

```{r, warning=FALSE, message=FALSE}
base <- h_alldat %>%
  plot_ly(x = ~GDP, y = ~H_score, 
          text = ~Country, hoverinfo = "text",
          width = 800, height = 500, size = 2) 

base %>%
  add_markers(color = ~Region, frame = ~Year, ids = ~Country) %>%
  animation_opts(1000, easing = "elastic", redraw = FALSE) %>%
  animation_slider(
    currentvalue = list(prefix = "YEAR ", font = list(color="red"))
  ) 

```


<br>  

## World Map by Happiness Scores

```{r, warning=FALSE, message=FALSE}
world_map <- map_data("world")
world <- world_map %>%
  dplyr::rename(Country = region) %>%
  dplyr::mutate(Country = str_to_lower(Country),
         Country = ifelse(
            Country == "usa",
            "united states", Country),
         Country = ifelse(
            Country == "democratic republic of the congo",
            "congo (kinshasa)", Country),
         Country = ifelse(
            Country == "republic of congo",
            "congo (brazzaville)", Country),
         Country = as.factor(Country))

h_alldat_world <- left_join(h_alldat, world, by = "Country",all.x=TRUE)

p <- ggplot(h_alldat_world, aes(long, lat, group = group,
                                fill = H_score,
                                frame = Year))+
  geom_polygon(na.rm = TRUE)+
  scale_fill_gradient(low = "white", high = "#FD8104", na.value = NA) +
  theme_map()

p %>%
  plotly::ggplotly() %>%
  animation_opts(1000, easing = "elastic",transition = 0,  redraw = FALSE)


```

# Regressions

```{r, warning=FALSE, message=FALSE, results='asis'}
country_formula <- H_score ~ GDP + Family + Health + Freedom + Generosity
country_model <- lm(country_formula, data = h_p_alldat)

stargazer(country_model, type = "html", omit = c("Constant"))

```
<br>  
<br>  

## Noticable Relationships: GDP & Freedom

```{r, warning=FALSE, message=FALSE}
colors <- c("Fredom" = "red", "GDP" = "blue")

ggplot(data = h_alldat)+
  geom_smooth(aes(x = Freedom, y = H_score, color = 'Freedom'), method = "lm")+
  geom_point(aes(x = Freedom, y = H_score, color = 'Freedom'), alpha = .3)+
geom_smooth(aes(x = GDP, y = H_score, color = 'GDP',), method = "lm")+
  geom_point(aes(x = GDP, y = H_score, color = 'GDP'), alpha = .3)

```





