---
title: "Self-Evaluation Project"
author: "Andy"
date: "3/13/2022"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float:
      smooth_scroll: false
---

<br>  

# Project Description

<br>  

<font size="3">   Towards the end of my military service, I tried to find ways to maintain a high-disciplinary lifestyle even after my release. After much contemplation, I decided to develop a grading system for my day-to-day life, which sprouted from the concept of math exams. The graded exams allow us to improve our mathematical knowledge by analyzing our weaknesses and strengths. Thus, by utilizing quantifiable variables that best represent the fullness of my lifestyle and by implementing various mathematical models, I was able to construct an effective grading system for my day-to-day life. 
    
  The self-evaluation project comprises three main procedures: collecting meaningful data, applying statistical analysis, and visualizing indicative findings in daily life. The goal is to find numerous insights and unique patterns with over 500 days' worth of data using R. Also, a more comprehensive understanding of the lifestyle will be obtained by utilizing advanced statistical concepts such as linear regressions and various correlation tests. Ultimately, these findings will provide better guidance for me to achieve healthier life patterns in the future.</font>


<br>  


```{r, results='hide', message=FALSE}
library(lubridate)
library(gridExtra)
library(margins)
library(psych)
library(grid)
library(forecast)
library(papeR)
library(tidyverse)
theme_set(theme_classic())
```



```{r, echo=FALSE}

all_dat = read.csv('/Volumes/Programming/Spring 2022/project/all_dat.csv')
# all_dat = read.csv('D:/Spring 2022/Project/all_dat.csv')
morning_rt = read.csv('/Volumes/Programming/Spring 2022/Project/morning_routine.csv')


colnames(all_dat) <- c('X', 'Name','Finished','Multiple','Phone_pickups',
                       'Screen_time','Date','Drink',
                       'Meditation','Mentality','Satisfaction',
                       'Reading','Productivity','Rise_time','Run','Social',
                       'Tech','Total','Total_todo','Work_done', 'Key_words')


# Remove unnecessary columns & Modify some columns
all_dat <- all_dat %>%
  select(Date, everything(), Finished, Total_todo,-X,-Name, - Work_done) %>%
  mutate(work_finished = round(Finished/Total_todo,4),
         Drink = lag(Drink),
         Total = Total*100) %>%
  filter(Multiple < 6) %>%
  tibble()

# Same for morning routine #new
morning_rt <- morning_rt %>%
  mutate(morning_phone = rise_time_check, # modify column name 
         night_phone = before_sleep_check) %>%
  select(Date, everything(), -c(X, level_0, index, 
                                rise_time_check, before_sleep_check)) %>%
  tibble()

```



```{r, echo=FALSE}
# Break dates
  # Fall, Thanksgiving, Christmas, Spring, Summer, etc.
date_breaks <- as.character(format(c(
seq(as.Date('2020-11-25', format = "%Y-%m-%d"), by = "day", length.out = 5),
seq(as.Date('2020-12-17', format = "%Y-%m-%d"), by = "day", length.out = 46),
seq(as.Date('2021-03-23', format = "%Y-%m-%d"), by = "day", length.out = 6),
seq(as.Date('2021-04-23', format = "%Y-%m-%d"), by = "day", length.out = 6),
seq(as.Date('2021-05-19', format = "%Y-%m-%d"), by = "day", length.out = 104),
seq(as.Date('2021-10-11', format = "%Y-%m-%d"), by = "day", length.out = 2),
seq(as.Date('2021-12-21', format = "%Y-%m-%d"), by = "day", length.out = 37),
seq(as.Date('2022-03-14', format = "%Y-%m-%d"), by = "day", length.out = 7)),
"%Y-%m-%d"))

# Semester Quarters
# 1st quarter of the semester
first_q <- c(as.character(format(c(
  seq(as.Date('09-01', format = "%m-%d"), by = "day", length.out = 27),
  seq(as.Date('02-01', format = "%m-%d"), by = "day", length.out = 27)),"%m-%d")))

# 2nd quarter of the semester
second_q <- c(as.character(format(c(
  seq(as.Date('09-28', format = "%m-%d"), by = "day", length.out = 27),
  seq(as.Date('02-28', format = "%m-%d"), by = "day", length.out = 27)),"%m-%d")))

# 3rd quarter of the semester
third_q <- c(as.character(format(c(
  seq(as.Date('10-25', format = "%m-%d"), by = "day", length.out = 27),
  seq(as.Date('03-27', format = "%m-%d"), by = "day", length.out = 27)),"%m-%d")))

# 4th quarter of the semester
fourth_q <- c(as.character(format(c(
  seq(as.Date('11-21', format = "%m-%d"), by = "day", length.out = 26),
  seq(as.Date('04-23', format = "%m-%d"), by = "day", length.out = 27)),"%m-%d")))

# Create School variable
all_dat <- all_dat %>%
  mutate(
    School = ifelse(
      format(as.Date(strptime(all_dat$Date, "%Y-%m-%d")), "%m-%d") %in% first_q, "1st", FALSE),
    School = ifelse(
      format(as.Date(strptime(all_dat$Date, "%Y-%m-%d")), "%m-%d") %in% second_q, "2nd", School),
    School = ifelse(
      format(as.Date(strptime(all_dat$Date, "%Y-%m-%d")), "%m-%d") %in% third_q, "3rd", School),
    School = ifelse(format(as.Date(strptime(all_dat$Date, "%Y-%m-%d")), "%m-%d") %in% fourth_q, "4th", School),
    School = ifelse(Date %in% date_breaks, "Break", School),
    School = ifelse(Date == '2021-08-30', "1st", School),
    School = ifelse(Date == '2021-08-31', "1st", School),
    School = ifelse(Date %in% c('2021-12-17','2021-12-18','2021-12-19','2021-12-20'), "4th", School),
    School = ifelse(Date %in% c("2022-01-27","2022-01-28"), "1st",School),
    Weekdays = weekdays(as.Date(Date,'%Y-%m-%d')),
    date_sep = Date
  ) %>%
  separate(date_sep, into = c("year", "month", "day"), sep="-") # Create year, month, day variables

# merge morning_rt with all_dat
all_morning_rt <- merge(morning_rt, all_dat,by="Date", all.x=T) %>%
  mutate(Date = ymd(Date),
         work_finished_mr_exc = 
           round((Finished-total_checked)/(Total_todo-6),4)) %>%
            # work_finished_mr_exc: this variable excludes morning routine 
            #         tasks for more accurate statistical analysis. 
  filter(work_finished_mr_exc <= 1 & work_finished_mr_exc >0) %>%
  arrange(desc(Date)) %>%
  tibble()


```

  
<br>  

# Main Variables: Descriptive Statistics

---

<br>  


```{r, echo = FALSE, eval = TRUE, fig.width = 7, fig.height = 7, warning = FALSE, fig.align='center'}

p1 <- ggplot(data = all_dat, alpha=.5) + 
  geom_density( aes(Total), color = 'red')

p2 <- ggplot(data = all_dat) +
  geom_density( aes(Multiple), color = 'blue')

p3 <- ggplot(data = all_dat, alpha=.5)+
  geom_density( aes(Reading), color = 'purple')

p4 <-ggplot(data = all_dat, alpha=.5)+
  geom_density(aes(Meditation), color = 'black')

p5 <- ggplot(data = all_dat, alpha=.5)+
  geom_density(aes(Phone_pickups), color = 'green')

p6 <- ggplot(data = all_dat, alpha=.5)+
  geom_density(aes(Screen_time), color = 'orange')

p7 <- ggplot(data = all_dat, alpha=.5)+
  geom_density(aes(Rise_time), color = 'skyblue')

p8 <- ggplot(data = all_dat, alpha=.5)+
  geom_density(aes(Drink), color = 'darkgreen')

p9 <- ggplot(data = all_dat, alpha=.5)+
  geom_density(aes(work_finished), color = 'darkgreen')

p10 <- ggplot(data = all_dat, alpha=.5)+
  geom_density(aes(Total_todo), color = 'darkgreen')
  
grid.arrange(p1, p2, p3,p4,p5,p6,p7,p8,p9,p10, nrow = 5,
             top = textGrob("Density Distribution for the Main Variables\n",gp=gpar(fontsize=16,font=1)))

```
<br>  

## Main Varibles Descriptions

* <font size="3">**Reading**: reading duration in minutes</font>
* <font size="3">**Meditation**: meditation duration in minutes</font>
* <font size="3">**Phone_pickups**: number of times I picked up my phone</font>
* <font size="3">**Screen_time**: duration of spent time on my phone in minutes</font>
* <font size="3">**Rise_time**: the variation in minutes from the intended rise time
    + 0: Woke up on time
    + -n: Woke up n minutes earlier than intended
    + +n: Woke up n minutes later than intended</font>
* <font size="3">**Drink**: Whether or not I drank the day before (Boolean)</font>
* <font size="3">**Work_finished**: Finished_tasks / Total_tasks </font>
* <font size="3">**Multiple**: Subjective grade given each day
    + Considered factors: Mentality, Satisfaction, Productivity, Social interaction, and Tech consumption</font>
* <font size="3">**Total**: The sum of the percentages calculated of above variables</font>

<br>  
<br>  

## Main Variables Correlations

<font size="4">To find the relationships between these variables and how they affect my lifestyle, we will first observe the relationships within variables</font>

* <font size="3">Use **pairs.panels function** in psych module
  + **The diagonal histograms** demonstrates the distribution of each variable 
  + **The bottom left triangle** represents a scatter plot with the best fit line
  + **The top right triangle** represents a correlation coefficient for each pair, which ranges from -1 to 1
      - If the coefficient is close to 1, it means that the pair holds a positive relationship and a negative relationship for -1. 
  + Correlation Coefficient Formula:</font>
$$r = \dfrac{\sum(x_i-\bar{x})(y_i-\bar{y})}{\sqrt{\sum(x_i-\bar{x})^2\sum(y_i-\bar{y})^2}}$$

<br>  


```{r, echo = TRUE, eval = TRUE, fig.width = 9, fig.height = 5, fig.asp = .75,  warning = FALSE}
correlation_plot <- all_dat %>%
  select(c(Screen_time, Meditation, Multiple, Rise_time, 
           Reading,Phone_pickups, work_finished, Total))

pairs.panels(correlation_plot, lm = TRUE)
```

<br>  



## School Variable
```{r, echo = TRUE, eval = TRUE, fig.width = 7, fig.height = 5, warning = FALSE}
ggplot(data = filter(all_dat, School != FALSE), aes(x = work_finished,
                           color = School))+
  geom_density()+
  labs(title = "Density Plot of Work Finished% for different School periods",
       x = "Work Finished (%)")+
  theme(plot.title = element_text(face = "bold")) +
  scale_color_discrete(name = "School Qtrs")
```
<br>  
<br>  
<br>  


## Weekday Variable
```{r, echo = TRUE, eval = TRUE,   warning = FALSE}

all_dat$Weekdays <- factor(all_dat$Weekdays,levels = c("Monday", "Tuesday", "Wednesday", "Thursday","Friday","Saturday","Sunday"))

ggplot(data = all_dat)+
  geom_boxplot(aes(x = Weekdays,
                   y = work_finished, color = Weekdays))+
  theme(legend.position = "None")+
  labs(title = "Work finished % by week days",
       subtitle = "Data: all_dat (500+ observations)",
       x = "", y = "Work Finished (%)")+
  theme(plot.title = element_text(face = "bold"))
```
<br>  
<br>  


## Time Trend (Total %)
```{r, echo = TRUE, eval = TRUE, fig.width = 7, fig.height = 5, warning = FALSE, message=FALSE}
all_dat_month <- all_dat %>%
  filter(!is.na(Rise_time)) %>%
  group_by(year, month) %>%
  dplyr::summarise(Total = mean(Total),
            Rise_time = mean(Rise_time)) %>%
  mutate(Date = make_date(year, month)) %>%
  arrange(Date)
  
  
ggplot(all_dat_month)+
  geom_line(aes(x=Date, y=Total))+
  labs(title = "Trend of Total%",
              subtitle = "Grouped by Month Average")+
  theme(plot.title = element_text(face = "bold")) +
  scale_x_continuous(breaks = ymd("2020-09-01", "2021-01-01","2021-04-01", "2021-07-01", "2021-10-01","2022-01-01", "2022-04-01"),
                     labels=c("09/20", "01/21", "04/21", "07/21", 
                                "10/21", "01/22","04/22"))
  

```

<br>  
<br>  


## Time Trend (Total % - Rise time)
```{r, echo = TRUE, eval = TRUE, fig.width = 7, fig.height = 5, warning = FALSE, message=FALSE}
ggplot(all_dat_month)+
  geom_line(aes(x=Date, y=Total-Rise_time))+
  labs(title = "Trend of Total% - Rise time",
              subtitle = "Larger positive differnce indicates higher productivity")+
  theme(plot.title = element_text(face = "bold")) +
  scale_x_continuous(breaks = ymd("2020-09-01", "2021-01-01", "2021-06-01",
                                "2022-01-01"))
  
```
<br>  

* <font size="3">Note for Rise time: 
    + 0: Woke up on intended time
    + Positive value: Later than intended
    + Negative value: Earlier than intended</font>
<br>  

<br>  

<br>  

<br>  



# Morning Routine Varables: Descriptive Statistics

---

<br>  

$$"The\ notion\ that\ once\ you\ set\ accomplishment\ in\ motion,\\ you\ can\ keep\ it\ in\ motion\ with\ much\ less\ effort\ than\\ if\ you\ were\ trying\ to\ accomplish\ something\ from\ a\ standing\ start."\\ -Jim\ Kwik$$
<br>  
<br>  


```{r, echo = FALSE, eval = TRUE, fig.width = 8, fig.height = 9, warning = FALSE, fig.align='center'}
# Total_checked: the number of morning routine tasks completed
mr_p1 <- ggplot(data = all_morning_rt) +
  geom_bar(aes(x = total_checked), fill = "orange",
           alpha = .8)+
  theme(legend.position = "None")

# Meditation_check: Meditation task completion (Boolean value)
mr_p2 <- ggplot(data = all_morning_rt) +
  geom_bar(aes(x = meditation_check, fill = meditation_check),
           alpha = .8)+
  theme(legend.position = "None")

# Reading_check: Reading task completion (Boolean value)
mr_p3 <- ggplot(data = all_morning_rt) +
  geom_bar(aes(x = reading_check, fill = reading_check),
           alpha = .8)+
  theme(legend.position = "None")

# morning_thoughts_check: Morning journal task completion (Boolean value)
mr_p4 <- ggplot(data = all_morning_rt) +
  geom_bar(aes(x = morning_thoughts_check, fill = morning_thoughts_check),
           alpha = .8)+
  theme(legend.position = "None")

# push_up_check: Push up task completion (Boolean value)
mr_p5 <- ggplot(data = all_morning_rt) +
  geom_bar(aes(x = push_up_check, fill = push_up_check),
           alpha = .8)+
  theme(legend.position = "None")

# Morning_phone: Did not touch my phone for the first hour of the day (Boolean value)
mr_p6 <- ggplot(data = all_morning_rt) +
  geom_bar(aes(x = morning_phone, fill = morning_phone),
           alpha = .8)+
  theme(legend.position = "None")

# Night_phone: Did not touch my phone for the last hour of the day (Boolean value)
mr_p7 <- ggplot(data = all_morning_rt) +
  geom_bar(aes(x = night_phone, fill = night_phone),
           alpha = .8, position = "dodge")+
  theme(legend.position = "None")

grid.arrange(mr_p2, mr_p3,mr_p4,mr_p5,mr_p6,mr_p7,mr_p1, nrow = 4,
             top = textGrob("Distribution for the Morning Routine Variables\n",gp=gpar(fontsize=16,font=1)))

```
<br>  

<br>  


## Morning Routine Descriptions
Note that they are all discrete/ categorical variables
<br>  

* <font size="3">**Total_checked**: The number of morning routine tasks completed</font>
* <font size="3">**Meditation_check**: Meditation task completion (Boolean value)</font>
* <font size="3">**Reading_check**: Reading task completion (Boolean value)</font>
* <font size="3">**morning_thoughts_check**: Morning journal task completion (Boolean value)</font>
* <font size="3">**Push_up_check**: Push up task completion (Boolean value)</font>
* <font size="3">**Morning_phone**: Did not touch my phone for the first hour of the day (Boolean value)</font>
* <font size="3">**Night_phone**: Did not touch my phone for the last hour of the day (Boolean value)</font>


<br>  
<br>  



## Test how Total_checked variable affects the outcome of the day
* <font size = "4">The morning routine tasks:
  + Not touching my phone for at least 30 minutes the night before
  + Not touching my phone for an hour after I wake up
  + Exercise (Push up)
  + Meditation
  + Reading
  + Morning journal </font>
  
```{r, collapse=TRUE, fig.asp = .75,  warning = FALSE}

# see how number of morning routine checks affects the Total %
ggplot(filter(all_morning_rt, total_checked != 0)) + 
  geom_density(aes(Total))+
  facet_wrap(~total_checked)+
  labs(title = "Morning Routine checked & \nTotal %")

# see how number of morning routine checks affects the total todo lists checked
ggplot(filter(all_morning_rt, total_checked != 0)) + 
  geom_density(aes(work_finished_mr_exc))+
  facet_wrap(~total_checked)+
  labs(title = "Morning Routine checked & \n todo lists finished(excluding morning routine tasks)")
```


<br>  

<br>  

<br>  



# Main Variables: Linear Regressions

---

## Simple Linear Regression
* <font size = "3">Set:
  + x = Explanatory Variable
  + y = Dependent Variable
  + $\alpha$ = y-intercept
  + $\beta$ = slope </font>

* <font size = "3">lm() function:Fitting Linear Models
  1. Finds fitted line($\alpha$ & $\beta$) by using the least-square method
      - **Least-square**: by summing up the residual squares for different curves, it finds the "least squared" curve that best fit the data. 
  2. Outputs $R^2$, p-value and other meaningful calculations
      - $R^2$: It demonstrates how accurate the fitted line is to the data
      - Formula: $R^2 =1-\dfrac{Var(fit)}{Var(mean)}$ or $1-\dfrac{RSS}{TSS}$
      - Ex: If we get.8, it means that $x$ explains 60% of the variation in $y$</font>

<br>  

```{r, echo = TRUE, eval = TRUE, fig.width = 6, fig.height = 5, warning = FALSE, message=FALSE}
model <- lm(work_finished ~ Meditation, data = all_dat)
pretty_lm <- prettify(summary(model))
rmarkdown::paged_table(pretty_lm)
ggplot(all_dat,aes(x=Meditation, y=work_finished))+
  geom_smooth(method = "lm")+
  geom_point()+
  labs(title = "Linear Regression",
       subtitle = "y = Total to-do lists finished (%) \nx = Meditation in minutes",
       y = "Total to-do lists finished (%)", x = "Meditation in minutes")+
  theme(plot.title = element_text(face = "bold"))
```
  
  
```{r, echo = TRUE, eval = TRUE, fig.width = 6, fig.height = 5, warning = FALSE, message=FALSE}
model <- lm(work_finished ~ Screen_time, data = all_dat)
pretty_lm <- prettify(summary(model))
rmarkdown::paged_table(pretty_lm)
ggplot(all_dat,aes(x=Screen_time, y=work_finished))+
  geom_smooth(method = "lm")+
  geom_point()+
  labs(title = "Linear Regression",
       subtitle = "y = The number of Phone pickups\nx = Rise time",
       y = "Number of Phone pickups\n", x = "\nRise time")+
  theme(plot.title = element_text(face = "bold"))
```

<br>  
<br>  
<br>  

## Multiple regressions
* <font size = "3">Set:
  + y = Dependent Variable
  + $x_1,...x_n$ = n independent/explanatory variables
  + $\alpha$ = Constant or intercept
  + $\beta$ = weights for each $x_1,...x_n$ </f   ont>
  
  
```{r, echo = TRUE, eval = TRUE, fig.width = 6, fig.height = 5, warning = FALSE, message=FALSE}
model <- lm(work_finished ~ Screen_time + Meditation + Rise_time + Phone_pickups + 
              Reading + Drink + Total_todo + Social,  data = all_dat)

pretty_lm <- prettify(summary(model))
rmarkdown::paged_table(pretty_lm)

```
<br>  
<br>  


## Actual vs Prediction Visualization for Work_done (all_dat)

```{r, warning=FALSE, message=FALSE}
all_dat$pred_work_finished <- predict(model, newdata = all_dat)

# Explanatory variable: work_finished
ggplot(data = all_dat, aes(x = pred_work_finished, y = work_finished)) +
  geom_point(alpha = 0.5, color = "darkgray") +
  geom_smooth(color = "darkblue") +
  geom_line(aes(x = work_finished,
                y = work_finished),   # Plotting the line, y = x
            color = "red", linetype = 2) +
  coord_cartesian( xlim = c(0, 1),
                   ylim = c(0, 1) ) +  # Limits the range of the
  labs(title = "Multiple Regression",
       subtitle = "Actual Tasks Finished (%) vs Predicted Values of Task Finished (%)",
       y = "Tasks Finshed (y)", x = expression(hat(y)))+
  theme(plot.title = element_text(face = "bold"))

```
<br>  

- Systematic Error can be observed
    - NOT a perfect prediction model, but the the model is reasonably accurate



```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
model_logit <- glm(work_finished_mr_exc ~ night_phone,
                   data = all_morning_rt, family = binomial(link = "logit"))
m = margins(model_logit) 
ame_result = summary(m) 
ame_result
```
<br>  

<!-- <font size="4">**Interpretation of the Average Marginal Effect(AME)**</font>

* <font size = "3"> Interpret them as percentage points rather than percentage
  + work_finished AME of .19 : Indicates that if I do not touch my phone the night before, I am 19.06 percentage point more likely to get more tasks done. </font>
<br>   -->

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.show='hide'}
ggplot(data = ame_result) +
  geom_point(aes(factor , AME)) +
  geom_errorbar(aes(x = factor, ymin = lower, ymax = upper),
  width = .5) + geom_hline ( yintercept = 0) +
  theme_minimal ( ) +
  theme(axis.text.x = element_text(angle = 90))
```


  
<br>  
<br>  

# Main Variables: Time Series
<br>  

```{r, message=FALSE, warning=FALSE}

ats <- ts(all_dat, start = decimal_date(ymd("2020-09-01")),
                            frequency = 365.25 / 7)

ggplot(data = all_dat) +
  geom_line(aes(x = ymd(Date), y = Total))+
  geom_smooth(aes(x = ymd(Date), y = Total, color = "red")) + 
  scale_x_continuous(breaks = ymd("2020-09-01", "2021-01-01","2021-04-01", "2021-07-01", "2021-10-01","2022-01-01", "2022-04-01"),
                     labels=c("09/20", "01/21", "04/21", "07/21", 
                                "10/21", "01/22","04/22"))+
  labs(title = "Time Seires", subtitle = "Total (%)")
  theme(legend.position = "None")
```

```{r, message=FALSE, warning=FALSE}
myts <- ts(all_dat$Total, start=c(2020, 9,1), end=c(2022, 3, 31), frequency=365)
fit = ets(myts)
plot(fit)
```

<br>  

```{r, echo = TRUE, eval = TRUE, fig.width = 10, fig.height = 7,  warning = FALSE, message=FALSE}

box_dat <- all_dat %>%
  group_by(month) %>%
  mutate(my = make_date(year, month)) %>%
  filter(!is.na(work_finished)) %>%
  group_by(my) %>%
  mutate(productivity_scale = mean(work_finished)) 

# Total months 
tot_month = length(unique(box_dat$my))

dates = seq(as.Date('2020-09-15', format = "%Y-%m-%d"), 
            by = "month", length.out = tot_month)
dates_lb = format(seq(as.Date('2020-09-01', format = "%Y-%m-%d"), 
                      by = "month", length.out = tot_month), "%m\n%y")

ggplot(box_dat) +
  geom_boxplot(aes(x = ymd(Date), y = Total, 
                   fill = productivity_scale, group = my))+
  labs(title = "Time Seires", subtitle = "Total (%) & Productivity\n", x = "Dates") +
  
  scale_x_date(breaks = dates, labels = dates_lb)+
  scale_fill_gradient(low = "white", high = "#C03B3B")+
  theme(plot.title = element_text(face = "bold"), legend.position = "bottom")
  
```

